Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-30 paper/lostanlenRelevanceScattering.tex
update intro of Supp material

\section{Supplementary material: }

The introductory paper on Gammatone wavelet \cite{Venkitaraman2014} does not provide a formula for deducing $\sigma$ from the specification of a quality factor $Q$.

In this appendix, we provide a rationale for choosing the topmost center frequency $\xi$ of a Gammatone wavelet filter bank in a discrete-time setting. Then, we relate the bandwidth parameter $\sigma$ to the choice of a quality factor Q.

>>>>

\section{Supplementary material}

The asymmetric amplitude profile of the Gammatone function makes it suitable to model temporal masking in auditory filterbanks.
Yet, the introductory paper on Gammatone wavelets \cite{Venkitaraman2014} does not provide a formula for deducing $\sigma$ from the specification of a quality factor $Q$.
In this appendix, we provide a rationale for choosing the topmost center frequency $\xi$ of a Gammatone wavelet filter bank in a discrete-time setting. Then, we relate the bandwidth parameter $\sigma$ to the choice of a quality factor Q.
